---
title: "BIOS6621-Homework8-Randy"
author: "Randy"
date: "11/19/2019"
output: word_document
---

#### Question1
```{r}
Alfuzo <- c(1,1,2,2,3,1,0,3,3,2,5,2,1,3,2,1,1,2,1,2,2,2,2,1,1,5,1,2,3,1,2,5,1,5,3,3,3,2,5,2,3,4,3,4,5,3,4,3,2,3,5,2,2,3)
NonAlfuzo <- c(10, 7, 4, 4, 3, 5, 6, 7, 7, 3, 5, 2, 4, 4, 6, 3, 6, 2, 5, 3, 5, 2, 4, 2, 3, 6, 4, 5, 4, 7, 4, 3, 3, 4, 2, 4, 4,3)

hist(Alfuzo, main = "Alfuzosin")
hist(NonAlfuzo, main = "Off Alfuzosin")
```
```{r}
par(mfrow=c(1, 2))
boxplot(Alfuzo, main = "Alfuzosin")
boxplot(NonAlfuzo, main = "Off Alfuzosin")
```
```{r}
wilcox.test(Alfuzo, NonAlfuzo)
```

Both distributions are not normal and right skewed. 
There is also outlier in the “Non-Alfuzosin” group.
Hence the nonparametric test would be appropriate. 
The Wilcoxon Rank Sum Test provides a p-value that is <0.05; this result shows that there is a statistically signifiant difference between the groups of Alfuzosin and Non-Alfuzosin. 
We need to consider the side effects besides make decisions about whether actually use Alfuzosin.

