---
title: "BIOS6621-Homework2-20190909"
author: "Randy"
date: "9/9/2019"
output:
  html_document:
    df_print: paged
  word_document: default
---
# **BIOS6621** *Homework2* 
## Basic Graphing
### Question1: 
Ex 1:  Add a red horizontal line at mean(y1) and a blue horizontal line at mean(y2)

Ex 2:  Move the legend up on the graph so it looks better and add red and blue points in front of the text
```{r}
x <- c(1,3,4,6,9,10,11,14)
y1 <- c(102,101,89,92,81,80,75,72)
y2 <- c(88,85,81,80,76,71,66,64)
plot( x, y1, xlab = 'x label', ylab = 'y label', pch = 19, 
      type = "b", cex = 0.7, col = "red", lty = 4, lwd = 3,
      xlim = c(0, 15), ylim = c(60, 110) )
points( x, y2, pch = "o", cex = 1, col = "blue", lty = 1, 
      type = "b", lwd = 3 )
abline( h = mean(y1), cex = 0.7, lty = 1, col = "red", lwd = 3)
abline( h = mean(y2), cex = 0.7, lty = 1, col = "blue", lwd = 3)
legend( "topright", leg = c("Female", "Male"), 
        text.col = c("red", "blue"), col = c("red", "blue"),
        bty = "n", pch = c(19, 111), cex = c(1, 1) )

```
---

As shown in **Figure**, for x in the range of 0~15, there is a decline tendency of y in both genders. Both gender's y (y1 represents Female's; y2 represents Male's) decreases reponding to the increas of x. Comparatively, each Male's y (y2) is lower than its Female counterpart (y1), at certain given x. 

The mean function:
$$ \bar x  = \frac{1}{n} * \sum_{i=1}^{n}  x_{i} = \frac {x_{1}+ x_{2}+ \dots+ x_{n}}{n} $$

As shown in **Figure**, the red line shows the average of y for Female, y1 = `r paste(mean(y1))`; the blue line shows the average of y for Male, y2 =`r paste(mean(y2))`

***

### Question2:
The summary of x, y1, and y2 is shown below.  

```{r,results='asis',echo=FALSE}
library(knitr)
summary <- t(apply(cbind(x, y1, y2), 2, summary))
kable(summary)
```
---


