---
title: "BIOS6621-Homework3"
author: "Randy"
date: "9/24/2019"
output: word_document
---
```{r message=FALSE, warning=FALSE}
VAdata3 <- read.csv("C:/Users/Goodgolden5/Desktop/BIOS6621-Gary Grunwald/Week 04/VAdata3.csv")
str(VAdata3)
summary(VAdata3)
VAdata3$proced <- as.character(VAdata3$proced)
```


Based on the summary of dataset DVdata, I will assume *hospcode*, *preced*, *sixmonth*, and *asa* are categorical data; and *weight*, *height*, and *bmi* are continueous variables.  

I probably will change the data into related data type before further analysis, other than leave the data as integeric form.

There are few things we should pay more attention: 

- 1. For *hospcode*, *preced*, *sixmonth*, and *asa*, those are categorical data with integer-levels, so we do not want to see decimals or other type numiric data type here. There would be more detailed exams for these type of errors.


- 2. There are several NA missing data in several columns.  


- 3. Specifically for *proced*, I would assume the data should be binary varible, however the value of 2 show up. This might be just typo or maybe the data was collected for extra information, for example with both procedures or did it twice.



```{r}
qqnorm(VAdata3$weight)
qqnorm(VAdata3$height)
qqnorm(VAdata3$bmi)
```

_ _ _

Then we can exam the normality of *$weight*, *$height*, and *$bmi*; and there are several extram values. 


- 1. The BMI has few valules over 40, the max is 70, which seems impossible for real data. I would guess the mix used metric/imperial unit cause the problem.


- 2. I would comfirm the unit levels for the weight and height, then correct the errors.

```{r}
VAdata3[!complete.cases(VAdata3),]
```
There are a few individuals with missing values. Here I list out all the missing values. I probably will confirm with the researchers or make proper assumptions before the tests, other than delete the those data.
